The pollination trade-off

### 2019-04-09 paper/manuscript.Rmd
Add automatic counter of references (due to Ecology Letters requirement)
Add automatic counter of displays
Add running title

**Author for correspondence:** E. Fernando Cagua (efc29@uclive.ac.nz) - Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury, Private Bag 4800, Christchurch 8140, New Zealand

>>>>

**Running title:** The pollination trade off

**Number of displays:** `r readd(n_displays)$figures` figures; `r readd(n_displays)$tables` tables; `r readd(n_displays)$text_boxes` text boxes.

**Number of references:** `r readd(n_references)`
